---
title: "p8105_hw3_pc2853"
author: "pc2853"
date: "October 15, 2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
options(tibble.print_min = 5)

library(ggridges)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
devtools::install_github("thomasp85/patchwork")
library(patchwork)

```

------
#Problem 1
```{r}
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data(brfss_smart2010)
```
```{r}
brfss_smart2010 =
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response == c("Excellent", "Very good", "Good", "Fair", "Poor")) %>% 
  janitor::clean_names()  %>% 
  mutate(response = forcats::fct_relevel(response, c("Excellent", "Very good", "Good", "Fair", "Poor")))
```
#### In 2002, which states were observed at 7 locations?


```{r}
brfss_smart2010 %>% 
  group_by(locationabbr) %>% 
  summarize(n_locations = n_distinct(locationdesc))
```

Looking at the summarized result about the number of location in each states, the states that have 7 locations are CT, MT, NH, OR, UT.

####Make a “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.

```{r}
brfss_smart2010 %>% 
  group_by(year, locationabbr) %>% 
  summarize(n_locations = n_distinct(locationdesc)) %>% 
  ggplot(aes(x = year, y = n_locations, color = locationabbr)) + geom_line() +
  labs(
    title = "Number of locations in every states",
    x = "Year",
    y = "Number of locations",
    color = 'States'
    )  
```

I make a spaghetti plot using geom_line with defferent color within different states, which summarizing the number of locations in each states.

####Make a table showing, for the years 2002, 2006, and 2010, the mean and standard deviation of the proportion of “Excellent” responses across locations in NY State.

```{r}
brfss_smart2010 %>% 
  filter(year == c(2006, 2002, 2010), locationabbr == "NY", response == "Excellent") %>% 
  group_by(year) %>% 
  summarize(NYmean = mean(data_value, na.rm = TRUE), NYsd = sd(data_value, na.rm = TRUE)) %>% 
  knitr::kable(digits = 1)
  
```
I made a table containing the mean and standard deviaion of the proportion of excellent response of NY state in 2002, 2006, 2010 by using the data_value. 

####For each year and state, compute the average proportion in each response category (taking the average across locations in a state). Make a five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.

```{r}
brfss_smart2010 %>% 
  group_by(locationabbr,year,response) %>% 
  summarize(mean_proportion = mean(data_value)) %>% 
  ggplot(aes(x = year, y = mean_proportion, color = locationabbr)) + facet_grid(~ response) + geom_line() +
  labs(
    title = "The Distribution of state-level averages over time", 
    x = "Year",
    y = "Averages"
  )
```

#Problem2
```{r p2setup}
data(instacart)
```

```{r data cleaning}
instacart = 
  instacart %>% 
  janitor::clean_names()
  
```
The data instacart imported from online is a dataset with dimension `r dim(instacart)`. It recorded every users imformation with various aspects for example the number of orders and the product number, ordered by each order id of individual users. 
####How many aisles are there, and which aisles are the most items ordered from?
```{r}
instacart %>% 
  group_by(aisle) %>% 
  select(aisle_id, order_id) %>%
  summarize(n_orders = n()) %>% 
  arrange(desc(n_orders)) %>% head(1) 
 
  
```
In total there are `r nrow(distince(instacart, aisle_id))` aisles, where fresh vegetables are the most items ordered from. 

####Make a plot that shows the number of items ordered in each aisle. Order aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_items = n()) %>% 
  mutate(aisle =  forcats::fct_reorder(aisle, desc(n_items))) %>%
  ggplot(aes(x = aisle, y = n_items)) + geom_point() +
  scale_y_continuous(breaks = c(0, 1000, 10000, 100000, 200000), limits = c(0, 200000), labels = c("0", "1000","10000","100000","200000")) +
  labs(
    title = "the number of items ordered in each aisle", 
       x = "aisles",
       y = "number of items") +
  theme(axis.text.x = element_text(angle = 90, size = rel(0.5), hjust = 1)) 
       
```





